---
title: "Reddit Posts and Movie Gross Box Office"
---


## What is the daily GBO trendafter movie is released?
```{r}

gbo_post_df_long %>%
  filter(release_date >= "2015-05-01") %>%
  filter(series == "log_gbo_daily" & daysFromToRelease <=100) %>%
  na.omit() %>%
  ggplot(aes(x = daysFromToRelease, y = value)) +
  geom_point() +
  geom_smooth() + 
  theme_bw() +
  labs(title = "Decline in Daily GBO after release date", x = "Days After Release", y = "Log Daily GBO") +
  geom_vline(xintercept = 0, linetype="dotted", 
                color = "red", size=0.5) +
  scale_x_continuous(limits = c(0,100))
  

```

* Declining trend of daliy GBO after release date

## How number of posts on Reddit vary before and after release date?
```{r}

gbo_post_df_long %>%
  filter(release_date >= "2015-05-01") %>%
  filter(series == "log_num_posts" & daysFromToRelease <=100) %>%
  na.omit() %>%
  ggplot(aes(x = daysFromToRelease, y = value)) +
  geom_point() +
  geom_smooth() +
  geom_vline(xintercept = 0, linetype="dotted", 
                color = "red", size=0.5) +
  theme_bw() +
  labs(title = "Number of Reddit Posts before and after release date", x = "Days Before/After Release (day 0 is release date)", y = "Log Number Posts") 
  

  

```

* Number of posts increase as release date approaches, then declines. With the peak about 5 days after release date.


## Do more posts have an impact on how GBO declines? 
```{r}
# bin movies on num posts
total_movie_posts <- gbo_post_df_long %>%
  filter(release_date >= "2015-05-01") %>%
  filter(series == "num_posts" & daysFromToRelease <=100) %>%
  group_by(movie_name) %>% 
  summarise(sum_posts = sum(value, na.rm = TRUE))

total_movie_posts$posts_bin <- ifelse(total_movie_posts$sum_posts > 100, ">100 posts",
                                     ifelse(total_movie_posts$sum_posts >= 1, "1-100 posts", "0 posts"))

# visualize
gbo_post_df_long %>%
  filter(release_date >= "2015-05-01") %>%
  filter(series == "log_gbo_daily" & daysFromToRelease <=100) %>%
  inner_join(total_movie_posts, by = c("movie_name")) %>%
  na.omit() %>%
  ggplot(aes(x = daysFromToRelease, y = value, col = posts_bin)) +
  geom_point() +
  geom_smooth() + 
  theme_bw() +
  labs(title = "Decline in GBO after release date (binned by number of posts)", x = "Days After Release", y = "Log GBO") +
  geom_vline(xintercept = 0, linetype="dotted", 
                color = "red", size=0.5) +
  scale_x_continuous(limits = c(0,100))
  
  
```

* GBO of movies with more posts overall, declines sharply then flattens out
* For movies with lower number of posts, GBO keeps on declines at a steady rate


## Does increasing posts increase GBO?
```{r}
# Rolling gbo and posts: each row =>  each day and movie, gbo made till that day, number of posts till that day
gbo_post_df_na_zero <- gbo_post_df %>% mutate(gbo_daily = ifelse(is.na(gbo_daily), 0, gbo_daily),
                       num_posts = ifelse(is.na(num_posts), 0, num_posts)) 

gbo_post_df_na_zero_cumsum <- gbo_post_df_na_zero %>%
  arrange(movie_name, date) %>%
  group_by(movie_name) %>%
  mutate(gbo_daily_sum = cumsum(gbo_daily),
         num_posts_sum = cumsum(num_posts)) %>%
  ungroup() %>%
  mutate(daysFromToRelease = as.integer(daysFromToRelease),
         log_gbo_daily_sum = log(gbo_daily_sum+1),
         log_num_posts_sum = log(num_posts_sum+1))

  
gbo_post_df_na_zero_cumsum %>%
  filter(release_date >= "2015-05-01" & log_gbo_daily_sum > 0) %>%
  ggplot(aes(x = log_num_posts_sum, y = log_gbo_daily_sum)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw() +
  labs(title = "Positive association of increasing GBO as Number of Posts increase", x = "Log Number of Posts", y = "Log Daily GBO")


#num of movies: 34
gbo_post_df_na_zero_cumsum %>%
  filter(release_date >= "2015-05-01"  & log_gbo_daily_sum > 0) %>% distinct(movie_name)
```

## check significance and R^2
```{r}
reg_data2 <- gbo_post_df_na_zero_cumsum %>%
  filter(release_date >= "2015-05-01" & log_gbo_daily_sum > 0)
summary(lm(log_gbo_daily_sum ~ log_num_posts_sum, data = reg_data2))

```
